### 2017-03-29 paper/evaluation.tex
fixed sardine specs

%To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
%processor machine with eight virtual CPUs (four cores with two native
%threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr

To run our experiments, we used a dedicated server with eight cores
and 16 GB of memory, running Ubuntu 14.04 LTS Trusty Tahr (64-bit
version).  Software settings include \Comment{the Linux \emph{sysstat}
package to measure performance, }git to fetch subjects, Java 8 and
Maven 3.3.9 to build and test subjects. Our evaluation scripts depends
on Python 3.4 and Bash to execute and R to analyze the data.  For
replication, all source artifacts are publicly available at
\Fix{create gh-pages}, including supporting scripts (\eg, the script
that test subjects and generates the raw data), and the full list of
projects. \Comment{, and a \emph{Vagrantfile} to emulate our hardware
and all software dependencies.}

>>>>

To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
processor machine with eight virtual CPUs (four cores with two native
threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
(64-bit version).  Software settings include \Comment{the Linux
\emph{sysstat} package to measure performance, }git to fetch subjects,
Java 8 and Maven 3.3.9 to build and test subjects. Our evaluation
scripts depends on Python 3.4 and Bash to execute and R to analyze the
data.  For replication, all source artifacts are publicly available at
\Fix{create gh-pages}, including supporting scripts (\eg, the script
that test subjects and generates the raw data), and the full list of
projects. \Comment{, and a \emph{Vagrantfile} to emulate our hardware
and all software dependencies.}
